Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-02-01 paper/letter.tex
estimados de masa HI y masa dinamica

Interpretation by \citep{masshesse}.

\end{document}

>>>>

Interpretation by \cite{mashesse03}.

For an homogeneous sphere the HI optical depth can be written
as $\tau = \sigma_0 n s$, where $\sigma_0$ is the optical depth at the
line's center, $n$ is the number density and $s$ is the sistem's
size. 
This can be rewritten in terms of the gas' temperature $T$ and column
density $N_{H}$as $\tau = 3.31 \times 10^{-14} (10^{4}\mathrm{K}/T)^{1/2}
(N_{H}/\mathrm{atoms\ cm}^{-2})$.

This allows us to approximate the total hydrogen mass as
\begin{equation}
M_{H} = m_{H}  N_{H} D^{2} = 226\times \tau  \left(\frac{T}{10^4
  \mathrm{K}}\right)^{1/2}\left(\frac{D}{\mathrm{kpc}}\right)^2M_{\odot}
\end{equation}

On the other hand, we have an estimate for the dynamical mass from the
galaxy size $D$ and its rotational velocity $V$:

\begin{equation}
M_{T} = \frac{V^{2}D}{G} = 4.32\times10^{5}
\left(\frac{V}{\mathrm{km\ s}^{-1}}\right)^2\left(\frac{D}{\mathrm{kpc}}\right) M_{\odot}
\end{equation}
\end{document}
